There are no small Advantages: Reinforcement learning in near continuous time with Deep RelAtive Mixture of Advantages

### 2019-01-07 paper/icml_drau/icml_drau.tex
Some additions to the text

The exploration scheme used~\cite{ddpg}, which consists in adding an
\emph{Orhnstein-Ullenbeck}~\cite{orn-ull} process to actions, is naturally time
invariant in the sense that it is first defined as a time continuous stochastic
process, and that discretization of this process are used in practice. Indeed,
a continuous \emph{Orhnstein-Ullenbeck} process is defined as
\begin{equation}
	dx_t = - (x_t - \mu) \theta dt + \sigma \dbt
\end{equation}
and is naturally discretized by turning $d$'s into $\delta$'s, and using
the same $\deltat$ for both the learning algorithm and the exploration scheme.
Consequently, this exploration scheme can readily be used in continuous action
environments.

On the other hand, the usual exploration scheme used in discrete actions
Q-learning, $\varepsilon$-greedy exploration~\cite{sutton} is not time
invariant, in the sense that resulting state trajectories do not converge to a
well defined stochastic process as $\deltat \rightarrow 0$.

\subsection{Learning rates scalings}
\label{subsec:lr}

\subsection{Algorithms}
\label{subsec:algorithm}
We introduce two versions of \emph{Deep Advantage Updating} to cover both the
continuous and discrete action cases. Both relies on applying either DDPG or DQN
to the reparameterized Q-function and enforcing the identifiability of $A^\pi$ by
making sure that $\max_a A^\pi(s, a) = 0$, either approximately or exactly for all
states.
\begin{algorithm}[ht]
	\caption{Deep Advantage Updating (Discrete actions)}
	\input{dauc.tex}
\end{algorithm}

>>>>

The exploration scheme used~\cite{ddpg}, which consists in adding an
\emph{Ornstein-Uhlenbeck}~\cite{orn-uhl} process to actions, is naturally time
invariant in the sense that it is first defined as a time continuous stochastic
process, and that discretization of this process are used in practice. Indeed,
a continuous Ornstein-Uhlenbeck process is defined as
\begin{equation}
	dx_t = - (x_t - \mu) \theta dt + \sigma \dbt
	\label{eq:orn_uhl}
\end{equation}
and is naturally discretized by turning $d$'s into $\delta$'s, and using
the same $\deltat$ for both the learning algorithm and the exploration scheme.
Consequently, this exploration scheme can readily be used in continuous action
environments.

On the other hand, the usual exploration scheme used in discrete actions
Q-learning, $\varepsilon$-greedy exploration~\cite{sutton} is not time
invariant, in the sense that resulting state trajectories do not converge to a
well defined stochastic process as $\deltat \rightarrow 0$. As $\dt$ goes to $0$,
for any $\varepsilon$ independant of $\dt$, the behavior of state trajectories get
closer to that of a white noise.

To obtain a temporally coherent exploration scheme in discrete action environment
when using Q-learning we instead directly apply a discretization of a time continuous
stochastic process to the output of the approximate Q-function, and select actions
by maximizing the resulting perturbed Q-function. Typically, the approximate Q-function
values are also perturbed using a discretized Ornstein-Uhlenbeck noise.

\subsection{Algorithms}
\label{subsec:algorithm}
We introduce two versions of \emph{Deep Advantage Updating} to cover both the
continuous and discrete action cases. Both relies on applying either DDPG or DQN
to the reparameterized Q-function and enforcing the identifiability of $A^\pi$ by
making sure that $\max_a A^\pi(s, a) = 0$ for all states.

Both of these algorithms are off policy, and work by trying to minimize the
optimal bellman gap on the Q-function. Minimizing the optimal Bellman Gap in
an off policy setup amounts to minimizing the quantity
\begin{algorithm}[ht]
	\caption{Deep Advantage Updating (Discrete actions)}
	\input{dauc.tex}
\end{algorithm}

\subsection{Learning rates scalings}
\label{subsec:lr}
To provide invariance to change of time discretization, one also needs to make
sure that learning is possible in finite macroscopic time \TODO{The difference between
macroscopic and microscopic must be defined earlier}, and that learning
will take approximately as much macroscopic time for a coarse discretization than
for a fine grained discretization. These two requirements means that learning a
meaningful approximation of the advantage function as defined in~\ref{eq:adv},
i.e. an approximation that is correct at a precision independant of the time
discretization, should be possible with a number of samples of order at most
$\frac{1}{\deltat}$. If this requirement is not satisfied, as the
discretization timestep decreases, the macroscopic time needed to acquire
enough data samples to learn a meaningful advantage function increases, meaning
that with a very fine grained discretization, it would take a nearly infinite
time to learn something that is easily learnable in a coarse discretization.

Let us provide an informal derivation, in an on policy policy evaluation setup,
of the orders of magnitudes on the learning rates of both $A$ and $V$. An
example problem showing that these orders of magnitudes are indeed best case
scenarios if we want a general learning algorithm is given in the supplementary
material.

In an on policy policy evaluation setup, when $A$ and $V$ are learnt using
approximate TD(0), the update rules on $\theta_1$ and $\theta_2$ for a given
transition $(s, a, \delta r, s + \delta s)$ are
\begin{align}
	\theta_1 &\leftarrow \theta_1 + \eta (\delta r + \gamma^{\deltat} V(s + \delta s) - V(s)) \partial_{\theta_1} V(s)\\
	\theta_2 &\leftarrow \theta_2 + \eta (\deltat A(s, a) - \left(\delta r + \gamma^{\deltat} V(s + \delta s) - V(s)\right)) \partial_{\theta_2} A(s)
\end{align}
